Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus (Extended Version)

### 2025-04-10 paper/paper.tex
data availability

>>>>

\section*{Data-Availability Statement}
For reproduction, the software supporting the claims in this paper is archived on Zenodo \cite{schaefer_2025_15049780}. For reuse, the Agda implementation of \theoryabbv is available \href{https://github.com/maxsnew/grammars-and-semantic-actions/tree/PLDI25Artifact}{on GitHub}.
